---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# banana

<!-- badges: start -->
<!-- badges: end -->

The goal of banana is to measure everything in bananas.
Using bananas to measure things is on old meme that I still dearly love. At my recent
trip to New Zealand I took pictures with bananas to measure things all the time. WEIRD SENTANCE

But bananas are an interesting metric, and maybe show why the Brits and Americans just can't let
go of the feet: You are able to intuitively understand how big a banana is. 

It is a nice approximation. and so in this package everything returns in bananas and because I can't imagine 1.23 banana, everything gets rounded up or down to the nearest small or large banana.

## Installation

You can install the released version of banana from [CRAN](https://CRAN.R-project.org) with:

``` r
#install.packages("banana")
```

## Example

This is a basic example which shows you how to solve a common problem:
Turning ordinary sizes into banana approximations.

```{r example}
library(banana)
library(units)
macbook <- set_units(c(13, 13.3, 16), "in")
macbook
```


```{r example continued}
bananamac <- as_banana(macbook)
bananamac
data.frame(bananamac)
str(bananamac)
```


The interesting thing I'm trying to create here is a vector that behaves just like normal
double vectors but displays in bananas.

The values are still there, in metrics. 

```{r}
as.numeric(bananamac)
to_units(bananamac)
```



#### References

- The banana for scale meme started in 2005! <https://knowyourmeme.com/memes/banana-for-scale>



Please note that the 'banana' project is released with a
[Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
