---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Banana 🍌

<!-- badges: start -->
<!-- badges: end -->

The goal of banana is to measure everything in bananas.
Using bananas to measure things is on old meme that I still dearly love[1]. I still sometimes
take pictures with bananas for scale!

But bananas are an interesting metric, and maybe show why the Brittish and American people 
just can't seem to let 
go of the feet: You are able to intuitively understand how big a banana is. 

A banana is a nice approximation when precision is just not that important. And so in this package every banana vector has size bananas and because I can't imagine 1.23 banana, everything gets rounded up or down to the nearest small or large banana.

First how to install it and than how to use it:

## Installation

You can install the released version of banana from [CRAN](https://CRAN.R-project.org) with:

```{r, eval=FALSE}
#install.packages("banana") # not on cran
devtools::install_github("RMHogervorst/banana")
```

## Examples 🍌

This is a basic example which shows you how to solve a common problem:
Turning ordinary sizes into banana approximations.

For instance I'm working on a macbook from early 2015 which is 13 inch in diagonal, and according to a website the new models are 13.3 and 16 inches. As a european I don't understand these sizes, 
but I do understand bananas!

```{r example}
library(banana)
library(units)
```

```{r}
# create unit size vector.
macbook <- set_units(c(13, 13.3, 16), "in")
macbook
```

Let's turn these non-intuitive inches (thumb size?) into something recognizable:
bananas!

```{r example continued}
bananamac <- as_banana(macbook)
bananamac
```
The banana vector uses the {vctrs} package and tells us there are 3 items in this vector.
Two are the size of 2 small bananas and one is the size of 2 large bananas. 
Very clear what size that is!

bananas are just like normal vectors:
You can subset them.
```{r}
bananamac[2:3]
```

Turn them into dataframes
```{r}
data.frame(bananamac)
```

Or look at their structure
```{r}
str(bananamac)
```


The interesting thing I'm trying to create here is a vector that behaves just like normal
double vectors but displays in bananas.

The values are still there, in centimeter or in units (cm)

```{r}
as.numeric(bananamac)
to_units(bananamac)
```

But the values are displayed as whole bananas.

The underlying values are still there though:

```{r}
bananamac2 <- 1.23 * bananamac
bananamac2
```

The first element has not turned into 1.23 * 2 = 2.46 small bananas, but into 2 large
bananas. 

```{r}
bananamac[[1]]
bananamac2[[1]]
```

Because only the print method is changed not the underlying data.

```{r}
as.numeric(bananamac[[1]])
as.numeric(bananamac2[[1]])
```

Have fun with this package!

#### References  🍌

[1]: [The banana for scale meme started in 2005! <https://knowyourmeme.com/memes/banana-for-scale>](https://knowyourmeme.com/memes/banana-for-scale)


## Code of conduct
Please note that the 'banana' project is released with a
[Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
